Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-04-15 article.tex
Fix references

\subsection{pirouette's pipeline}\label{subsec:pipeline}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a phylogeny (1a) simulated by generative prior 
$\mathit{P}$.
    The phylogeny is converted to an alignment (2a) using alignment model 
$\mathit{A}$. 
    The user supplies one or more experiments.
    For each candidate experiment $\mathit{X}$ 
    (a tuple of inference model $\mathit{I}$ and condition $\mathit{C}$),
    if its condition $\mathit{C}$ is 
    satisfied (which can depend on the alignment), 
    it becomes a selected experiment $\mathit{X'}$, 
    to be used in the next step (3a).
    The inference models of the selected experiment use the alignment (2a) 
    to each create a Bayesian posterior of (parameter estimates and) 
    phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, a twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using twinning parameters $T$, where $T$ may depend on
    the experiments \richel{improve}.
    From a twin phylogeny, the same intermediate steps are taken,
    resulting in a twin error distribution (5b)
  \label{fig:pipeline}
\end{figure}

@@

\verb;pirouette; is free, libre and open source software available at 
\url{http://github.com/richelbilderbeek/pirouette},
licensed under the GNU General Public License version 3.
\verb;pirouette; depends on multiple packages, which are:
\richel{I think we can get rid of some dependencies, we just need to check}
\verb;ape; (\cite{APE}), 
\verb;babette; (\cite{bilderbeek2018babette}),
\verb;becosys; (\cite{becosys}),
\verb;DDD; (\cite{DDD}),
\verb;devtools; (\cite{devtools}),
\verb;geiger; (\cite{geiger}),
\verb;ggplot2; (\cite{ggplot2}),
\verb;knitr; (\cite{knitr}),
\verb;lintr; (\cite{lintr}),
\verb;mcbette; (\cite{mcbette}),
\verb;nLTT; (\cite{nLTT}),
\verb;PBD; (\cite{PBD}),
\verb;phangorn; (\cite{phangorn}),
\verb;phytools; (\cite{phytools}),
\verb;rappdirs; (\cite{rappdirs}),
\verb;rmarkdown; (\cite{rmarkdown}),
\verb;Rmpfr; (\cite{Rmpfr}),
\verb;stringr; (\cite{stringr}),
\verb;subplex; (\cite{subplex}),
\verb;TESS; (\cite{TESS}),
\verb;testit; (\cite{testit}), 
\verb;testthat; (\cite{testthat}) and
\verb;tidyr; (\cite{tidyr}).

>>>>

\subsection{pirouette's pipeline}
\label{subsec:pipeline}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline.
    The pipeline starts from a phylogeny (1a) simulated by generative prior 
    $\mathit{P}$.
    The phylogeny is converted to an alignment (2a) using alignment model 
    $\mathit{A}$. 
    The user supplies one or more experiments.
    For each candidate experiment $\mathit{X}$ 
    (a tuple of inference model $\mathit{I}$ and condition $\mathit{C}$),
    if its condition $\mathit{C}$ is 
    satisfied (which can depend on the alignment), 
    it becomes a selected experiment $\mathit{X'}$, 
    to be used in the next step (3a).
    The inference models of the selected experiment use the alignment (2a) 
    to each create a Bayesian posterior of (parameter estimates and) 
    phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, a twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using twinning parameters $T$, where $T$ may depend on
    the experiments.
    From a twin phylogeny, the same intermediate steps are taken,
    resulting in a twin error distribution (5b)
  }
  \label{fig:pipeline}
\end{figure}

@@

\verb;pirouette; is free, libre and open source software available at 
\url{http://github.com/richelbilderbeek/pirouette},
licensed under the GNU General Public License version 3.
\verb;pirouette; depends on multiple packages, which are:
\verb;babette; (\cite{bilderbeek2018babette}),
\verb;becosys; (\cite{becosys}),
\verb;DDD; (\cite{DDD}),
\verb;devtools; (\cite{devtools}),
\verb;geiger; (\cite{geiger}),
\verb;ggplot2; (\cite{ggplot2}),
\verb;knitr; (\cite{knitr}),
\verb;lintr; (\cite{lintr}),
\verb;mcbette; (\cite{mcbette}),
\verb;nLTT; (\cite{nLTT}),
\verb;PBD; (\cite{PBD}),
\verb;phangorn; (\cite{phangorn}),
\verb;phytools; (\cite{phytools}),
\verb;rappdirs; (\cite{rappdirs}),
\verb;rmarkdown; (\cite{rmarkdown}),
\verb;Rmpfr; (\cite{Rmpfr}),
\verb;stringr; (\cite{stringr}),
\verb;subplex; (\cite{subplex}),
\verb;TESS; (\cite{TESS}),
\verb;testit; (\cite{testit}), 
\verb;testthat; (\cite{testthat}) and
\verb;tidyr; (\cite{tidyr}).
